\section{Methods for Benchmarking Boolean Search Indexes}
To compare the boolean indexes, the indexing and search functions of each index were timed. Timing the code was done using Rust Criterion. When timing with Criterion, the cache is firstly warmed up for 3 seconds, which reduces the variance from each timing. After the cache is warmed up the same piece of code is run 100 times and the mean, the standard deviation and potential outliers are calculated. 

To compare the indexing time, the code that indexed the different search engines where timed using criterion. All search engines were indexed over different file sizes.

When comparing the search time, it was desired to test the search time over both varying file sizes and over varying depths of queries, as this would showcase the advantages and disadvantages of some search engines. Therefore multiple queries were generated. For each file size and for each depth 1000 queries were generated. To generate one query of depth $d$, $O(2^d)$ words and Boolean operators were found to fill in the query. With a $90\%$ change a word from the database of the file size where selected. Otherwise, the string "icantbefound" where selected as that string not is present in any of the files. The Boolean operaters where choosen uniformly. Thereby different queries were generated for each depth, but all queries were generated with the same seed, so the words and boolean operaters are selected in the same order.

For each file size and for each depth, searching for the 1000 queries were timed using Criterion.